GMSE: a general tool for management strategy evaluation

### 2017-09-15 notebook/presentation/GMSE_presentation.Rmd
Minor adjustments to the introduction

Image: [Janet Tench](https://commons.wikimedia.org/wiki/File:Norfolk_potato_field_-_geograph.org.uk_-_180521.jpg)
</center>

@@

>>>>

<br><br>

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; Image: [Janet Tench](https://commons.wikimedia.org/wiki/File:Norfolk_potato_field_-_geograph.org.uk_-_180521.jpg)

@@

<br><br><br>
